Management induced changes of soil organic carbon on global croplands

### 2020-12-14 ResultNotebooks/results_SOCscenario.Rmd
update figures

ci2plot <- c('Above Ground Residues'="ag.crop",          
             'Below Ground Residues'="bg.crop",          
             'Manure from Monogastrics'="livst_chick.crop",
             'Manure from Monogastrics'="livst_egg.crop",
             'Manure from Monogastrics'="livst_pig.crop",
             'Manure from Ruminants'="livst_milk.crop",  
             'Manure from Ruminants'="livst_rum.crop",   
             'Natural Litterfall and Fine Roots'="litfall.natveg")

@@

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color    ="Initalitzation",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:2], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

>>>>

ci2plot <- c('above-ground residues'="ag.crop",          
             'below-ground residues'="bg.crop",          
             'manure from monogastrics'="livst_chick.crop",
             'manure from monogastrics'="livst_egg.crop",
             'manure from monogastrics'="livst_pig.crop",
             'manure from ruminants'="livst_milk.crop",  
             'manure from ruminants'="livst_rum.crop",   
             'natural litterfall and fine roots'="litfall.natveg")

@@

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = expression(paste('Global \u0394SOC in GtC')),
        color    ="Initialization",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:2], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

### 2020-12-14 SOCbudgetPaper/SOCbudget.Rmd
update figures

acknowledgements: |
  Thanks to Vera Porwollik for contributing the time resolved tillage data set based on her previous work. Thanks to the rticles contributors. 
appendix: |

>>>>

acknowledgements: |
  Thanks to Vera Porwollik for contributing the time resolved tillage data set based on her previous work. Thanks to the rticles contributors as well. The authors thank for the data provided by FAOSTAT and LUH2v2. The work of Kristine Karstens was funded by the DFG Priority Program “Climate Engineering: Risks, Challenges, Opportunities?” (SPP 1689) and specifically the CEMICS2 project (grant no. ED78/3-2). The research leading to these results has received funding from the European Union’s Horizon 2020 research and innovation program under grant agreement no. 776479 (COACCH) and . This work was also supported by    funded by the German Federal Ministry of Education and Research (BMBF).

appendix: |

### 2020-12-14 SOCbudgetPaper/SOCbudget.tex
update figures

\% latex table generated in R 3.6.3 by xtable 1.8-4 package
\% Mon Dec 14 06:14:28 2020

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
Thanks to Vera Porwollik for contributing the time resolved tillage data set based on her previous work. Thanks to the rticles contributors.
\end{acknowledgements}

>>>>

\% latex table generated in R 3.6.3 by xtable 1.8-4 package
\% Mon Dec 14 21:01:55 2020

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
Thanks to Vera Porwollik for contributing the time resolved tillage data set based on her previous work. Thanks to the rticles contributors as well. The authors thank for the data provided by FAOSTAT and LUH2v2. The work of Kristine Karstens was funded by the DFG Priority Program ``Climate Engineering: Risks, Challenges, Opportunities?'' (SPP 1689) and specifically the CEMICS2 project (grant no. ED78/3-2). The research leading to these results has received funding from the European Union's Horizon 2020 research and innovation program under grant agreement no. 776479 (COACCH) and . This work was also supported by funded by the German Federal Ministry of Education and Research (BMBF).
\end{acknowledgements}
